SMT-Boosted Security Types for Low-Level MPC

### 2025-11-07 toplas26/sty.tex
checkpoint

As discussed in Section \ref{???}, a \emph{secret sharing scheme}
includes functions $\genshares$ and $\recon$ which generate
and reconstruct shares, respectively.
It is well-known that adding or subtracting a sample from a uniform
distribution in a finite field yields a value in a uniform
distribution, meaning that samples can be used as OTPs with
perfect secrecy \cite{barthe2019probabilistic,darais2019language}.
So we can define:
\begin{eqnarray*}
  \genshares(\phi) &\defeq& [\phi - \rx{y}{\cid_2}, \rx{y}{\cid_2}]\\
  \recon([\phi_1,\phi_2]) &\defeq& \phi_1 \fplus \phi_2
\end{eqnarray*}
where we require that $\genshares$ consumes the randomness
$\setit{\rx{y}{\cid_2}}$ for use as an OTP.

@@

The interactive share typing rules are defined in Figure \ref{fig-styinteractive},
with judgements of the form $\eqs \vdash \Gamma_1,R_1, \stredx \Gamma_2,R_2$.
Each such judgement establishes a sound type binding for interactively-defined
variables-- that is, unicast and broadcast messages exchanged between
clients. In addition to type bindings, judgments track random variables
used as OTPs, allowing us to use type linearity to enforce one-time
usage similar to previous related work \cite{darais2019language}.
To this end, in these rules we define $R_1 \uplus R_2$ as the disjoint
union of $R_1$ and $R_2$.

The \TirName{Share} rule generates the binding $[\mx{z}{\cid_2}, \rx{y}{\cid_1}]$
if this is a secret sharing as defined by $\genshares$. It also adds
$\rx{y}{\cid_1}$ to the set of variables used as OTPs, ensuring that
it has not already been used.

>>>>

As discussed in Section \ref{???}, a \emph{secret sharing scheme}
includes functions $(\genshares,\recon)$ which generate
and reconstruct shares, respectively.
It is well-known that adding or subtracting a sample from a uniform
distribution in a finite field yields a value in a uniform
distribution, meaning that samples can be used as OTPs with
perfect secrecy \cite{barthe2019probabilistic,darais2019language}.
So we can define:
\begin{eqnarray*}
  \genshares(\phi) &\defeq& [\phi - \rx{y}{\cid_2}, \rx{y}{\cid_2}]\\
  \recon([\phi_1,\phi_2]) &\defeq& \phi_1 \fplus \phi_2
\end{eqnarray*}
where we require that $\genshares$ consumes the randomness
$\setit{\rx{y}{\cid_2}}$ for use as an OTP.

@@

The interactive share typing rules are defined in Figure
\ref{fig-styinteractive}, with judgements of the form $\eqs \vdash
\Gamma_1,R_1, \stredx \Gamma_2,R_2$.  Each such judgement establishes
a sound type binding in $\Gamma_2$ for interactively-defined
variables-- that is, unicast and broadcast messages exchanged between
clients-- assuming the bindings in $\Gamma_1$. In addition to type
bindings, judgments track random variables used as OTPs, allowing us
to use type linearity to enforce one-time usage similar to previous
related work \cite{darais2019language}, where any randomness used in
the typing is not in $R_1$ and added to $R_2$. To this end, in these
rules $\uplus$ is disjoint union.

The \TirName{Share} rule generates the binding $[\mx{z}{\cid_2},
  \rx{y}{\cid_1}] : \sharety$ if this is a secret sharing as defined
by $\genshares$. It also adds $\rx{y}{\cid_1}$ to the set of variables
used as OTPs, ensuring that it has not already been used. The
\TirName{Reveal} rule generates the binding $\pubx{\px{x} + \px{y}} :
\outty$ with the requirement that $[\px{x},\px{y}]$ are typable as
shares. The \TirName{SecOpen} rule is similar except it allows the
assertion $\pubx{\px{x} + \px{y}} : \pubty$ if we can additionally
show that the shared value is masked by the use of random value
$\rx{z}{\oid}$ as an OTP. Here we are positing a third party $\oid$
that secret-shares $\rx{z}{\oid}$ as part of an initialization
protocol. We illustrate secure openings in practice at more length
in Section \ref{section-examples}, though we note that appropriate
properties of initialization protocols can be encoded in $\eqspre$.
